Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2017-10-12 TACAS2018/paper.tex
more on the numerical representation sec

Let $\mathbb{R}_{\langle M,F \rangle}$ be a fixed point domain with $M$ bits
representing the binary word length of the representation and $F$ bits
representing the prescaling $2^{-F}$ (\emph{i.e} the number of bits after
the decimal place).  We note that a negative $F$ denotes an integer
multiplication that adds $-F$ trailing zeros in the number represented by
$M$.  Let also $\mathbb{R}_{\langle M,[E] \rangle}$ be a floating point
domain with $M$ bits mantissa and $E$ bits exponent.  This domain
corresponds to $$\mathbb{R}_{\langle M,[E] \rangle} = \bigcup_F
\mathbb{R}_{\langle M,F \rangle} \mid F \in [2^{1-E}, 2^{E-1}]$$ This
definition important because it means that the distance between any two
numbers in the domain depends on the location of those numbers.  Since
%we have shown that
a floating point domain is a union of a number of fixed
point domains, we will continue our reasoning on fixed point only, which
will apply to the floating point domain by extension.  Operations on these
numbers will incur errors that can be bound
by~\cite{DBLP:conf/arith/BrainTRW15}.

@@

Let us first consider the effect of the quantization errors. 
Within the controller, state values are manipulated at low precision,
alongside the vector multiplication $\mat{K}\vec{x}$. Furthermore, 
the quantizers for the DAC and the ADC introduce truncation errors
which we denote by the effect of the functions $\mathcal{F}_{\langle D \rangle}$
and $\mathcal{F}_{\langle A \rangle}$ respectively. Finally, let us call $\vec{\nu}_e$ the
error caused by the FWL effects on the observer (\emph{i.e} the numerical errors 
in the calculations as opposed to the estimation error).
The inputs are computed using the following equation: 
%
\begin{align}
u_{k}&=\mathcal{F}_{\langle D \rangle}\left(-\mat{K}_{\langle C \rangle}\cdot\left(\mathcal{F}_{\langle C \rangle}\left(\mathcal{F}_{\langle A \rangle}(\vec{x}_{k})\right)\right) +\vec{\nu}_e\right)
\label{eq:uk}
\end{align}

This induces two types of the errors detailed above: first, the truncation
error due to the domain transformations $\mathcal{F}_{\langle *
\rangle}(\cdot)$; and second, the rounding error introduced by the
multiplication operation.  We represent these errors as non-deterministic
additive noise. More details can be found in Appendix~\ref{appendix:quantization}.

@@

$M$.  Let also $\mathbb{R}_{\langle M,[E] \rangle}$ be a floating point

>>>>

Let $\mathbb{R}_{\langle M,F \rangle}$ be a fixed point domain with $M$ bits
representing the binary word length of the representation and $F$ bits
representing the prescaling $2^{-F}$ (\emph{i.e} the number of bits after
the decimal place).  We note that a negative $F$ denotes an integer
multiplication that adds $-F$ trailing zeros in the number represented by
$M$.
\todo{why do we need to go into floating point?}
Let also $\mathbb{R}_{\langle M,[E] \rangle}$ be a floating point
domain with $M$ bits mantissa and $E$ bits exponent.  This domain
corresponds to $$\mathbb{R}_{\langle M,[E] \rangle} = \bigcup_F
\mathbb{R}_{\langle M,F \rangle} \mid F \in [2^{1-E}, 2^{E-1}]$$ This
definition important because it means that the distance between any two
numbers in the domain depends on the location of those numbers.  Since
%we have shown that
a floating point domain is a union of a number of fixed
point domains, we will continue our reasoning on fixed point only, which
will apply to the floating point domain by extension.  Operations on these
numbers will incur errors that can be bound
by~\cite{DBLP:conf/arith/BrainTRW15}.

@@

Let us first consider the effect of the quantization errors. 
Within the controller, state values are manipulated at low precision,
alongside the vector multiplication $\mat{K}\vec{x}$.
\todo{$\mathcal{F}$ is not clearly defined}
Furthermore, 
the quantizers for the DAC and the ADC introduce truncation errors
which we denote by the effect of the functions $\mathcal{F}_{\langle D \rangle}$
and $\mathcal{F}_{\langle A \rangle}$ respectively. Finally, let us call $\vec{\nu}_e$ the
error caused by the FWL effects on the observer (\emph{i.e} the numerical errors 
in the calculations as opposed to the estimation error).
The inputs are computed using the following equation: 
%
\begin{align}
u_{k}&=\mathcal{F}_{\langle D \rangle}\left(-\mat{K}_{\langle C \rangle}\cdot\left(\mathcal{F}_{\langle C \rangle}\left(\mathcal{F}_{\langle A \rangle}(\vec{x}_{k})\right)\right) +\vec{\nu}_e\right)
\label{eq:uk}
\end{align}

This induces two types of the errors: first, the truncation
error due to the domain transformations $\mathcal{F}_{\langle *
\rangle}(\cdot)$; and second, the rounding error introduced by the
multiplication operation.  We represent these errors as non-deterministic
additive noise. More details can be found in Appendix~\ref{appendix:quantization}.

@@

$M$.
Let also $\mathbb{R}_{\langle M,[E] \rangle}$ be a floating point
